% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{autonomous vehicles}{obstacle detection}{LiDAR}{point cloud}{multiple sensors fusion}
The activity in the area of autonomous vehicles navigation in recent years has initiated a series of reactions that stirred the automobile industry.Due to the LiDAR sensor's ability of providing a detailed understanding of the environment surrounding the vehicle, it has been widely used in a plethora of autonomous driving scenarios.The data type of LiDAR is point cloud. A factor that affect's the point cloud's vertical resolution is the number of LiDAR's beems.Point clouds achieved from a low-beams LiDAR can be very sparse and thus have a negative effect on the environmental perception, while high-beams LiDAR are extremely expensive, thus constrain the popularity of the technology of autonomous vehicles.

To solve the problem mentioned above, a novel mechanism is proposed in this paper. This mechanism reciprocate the low-beams LiDAR sensor in the heading direction through a crank-linker. Then, register all the point clouds during a period of the mechanism's motion to increase the vertical resolution of the point cloud. In addition, this paper proposes a method which recitifys the motion distortion of LiDAR by multiple lineary interpolation in a single point cloud, thus imporves the performance of multiple frame fusion.

Futhermore, to make the best of multiple sensors to detect obstacles in autonomous environment, camera image and LiDAR data are fused after calibing the LiDAR and cameras's extrins paramters.This paper also uses point cloud to optimize the performance of objection detection accuracy based on camera image.

To evaluate the mechanism proposed in this parper, a simulation in Gazebo was performed to simulate the multiple frames fused cloud.Then the mechanism was placed in an autonomous vehicle to construct a 3d map and segment obstacles in point clouds.This paper also evaluate the result of camera-LiDAR's calibration. The experiment shows that the mechanism can effectively improve the vetical resolution of the point cloud, which is three to four times of the 64-beams LiDAR. It's very significant for 3d mapping and obstacle detection in autonomous driving scenarios.
\end{Eabstract}
